\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{xcolor}
\definecolor{secondary}{HTML}{0D47A1}
\usepackage[T1]{fontenc}

\usepackage[pdfencoding=auto]{hyperref}

\pdfstringdefDisableCommands{%
  \def\faGraduationCap{\unichar{"F19D}}
  \def\faFlask{\unichar{"F0C3}}
  \def\aiGoogleScholar{\unichar{"E9D4}}
  \def\faPieChart{\unichar{"F200}}
  \def\faGears{\unichar{"F085}}
  %
}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
% \renewcommand{\section}[2]{\vspace{5pt}
%   \colorbox{secondary}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
% }

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\normalsize{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemNoColon}[2]{
  \item\normalsize{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNoColon}[2]{\resumeItemNoColon{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	 \textbf{{\Large Niraj Rajgor}} &
     \href{mailto:nirajr1992@gmail.com}{\faEnvelope \space nirajr1992@gmail.com}\\
     \faPhone \space +91 8097495277 &
     \href{https://www.linkedin.com/in/amanpreet-singh-k}{\faLinkedin \space /nirajrajgor}\\
\end{tabular*}

\vspace{8pt} % HACK
%-----------ABOUT-----------------
I have 5+ years of developing medium to large scale software while working in a startup environment.

%-----------EXPERIENCE-----------------
\section{{\faPieChart} Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Kustard Technologies}{Mumbai, India}
      {Senior Software Engineer}{Apr 2018 -- Apr 2020}
      \resumeItemListStart
       \resumeItem{Digital Signage} 
       {Developed SASS project that manages the Signage app on Raspberry pi from the Web Dashboard. My responsibilities included planning, managing the project, writing testable \& modular code. Achieved high performance by using techniques like code splitting \& lazy loading.}
       \resumeItem{Prodace}
       {Developed a SASS product that provides an online workspace for film productions. Worked on Websockets, Permission-based UI \& involved in the decision making of designs. Completed the project 15 days before the deadline which helped a client launch \& get feedback faster.}
       \resumeItem{Hbits}
       {Led the development of a mobile responsive real estate ownership platform. My responsibilities included writing modular code, developing APIs, code reviews, delegating the work, and timely delivery. Extended the library features to accommodate the design needs. Architected the code to achieve maximum reusability \& high performance at scale.}
       \resumeItem{Wings \& Wheels (Travel portal)}
       {Took full ownership to develop the flight booking platform and delivered it within the deadline. Accomplished flexibility, performance improvement, and less overhead by writing custom code rather than using the library. Implemented the pixel-perfect design.}
       \resumeItem{Simba}
       {Led the execution of Order tracking \& Analytical platform for a famous beer brand in India. My responsibilities include developing a dashboard, client communication, and managing team. Improved the performance for displaying tabular data from 3,000 records to 50,000 records by researching \& integrating a high-performance library.}
	   \resumeItemListEnd
      \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     \textit{\small Software Engineer} & \textit{\small Mar 2017 -- Mar 2018} \\
      \end{tabular*}\vspace{-5pt}
      \resumeItemListStart
        \resumeItem{Runners wall of fame(Marathon)}
        {Developed a web-based platform to analyse the statistical data \& provide personalized insights to the runners. Implemented the project in a tight deadline of 7 days \& made it work for a 10-foot screen. Used by more than 10,000 users during the marathon expo event.}
        \resumeItem{Snappbox}
        {Developed Customer and Admin platform for pickup \& delivery of logistics. Implemented key features like RTL for Arabic language, Partial saving of form data, and Allowing the user to add addresses from google maps. The platform moved the operations from offline to online which helped client save money every year.}
        \resumeItem{Kustard Website}
        {My primary role was to oversee and mentor other developers working on the project, manage the timeline, and perform code review. Accomplished timely delivery through combined efforts \& launched the website within 2 months. Achieved competitive advantage which helped business attract new clients.}
        \resumeItem{Exrup}
        {Developed a SASS product for Digital business card. Took full responsibility for design and development of dashboard. Challenged tackled include responsive business card layout, implementing color picker, implementing ReCaptacha an Excel export of data.}
      \resumeItemListEnd

      \vspace{2mm}
      \resumeSubheading
      {LiveFiesta}{Mumbai, India}
      {Frontend Developer}{July 2016 -- Jan 2017}
      \resumeItemListStart
      \item {Designed and developed PWA for Event Ticking platform in Angular 2. This helped in moving Ticket booking experience from offline to online.}
      \item {Took full responsibilities of the project and implemented the entire flow. Worked on Social Signup, Login, Search Events, Payment and Analytics modules.}
      \resumeItemListEnd

      \vspace{2mm}
      \resumeSubheading
      {TechGenium}{Mumbai, India}
      {Frontend Developer \& Co-Founder}{Jun 2015 -- May 2016}
      \resumeItemListStart
      \item {Developed web-based products addressing specific needs of small and medium scale businesses.}
      \item {Undertook project management responsibilities that included tasks like requirements analysis, project draft and proposal and tracking project timelines and deadlines.}
      \item {Actively involved in team building, interviewing candidates for technology roles and training new hires and mentoring interns.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{{\faGears} Technical Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{Languages \& DB}{Proficient in Javascript, ES6, CSS, \& HTML, Experience with Python, Node, MySQL, PHP}
 \resumeSubItem{Frameworks}{React, Redux, jQuery, Wordpress, Angular 2, SCSS, Bootstrap, Flask.}
 \resumeSubItem{Build \& Other Tool}{Git, Webpack, Bash, Linux.}
 \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------------
\section{{\faFlask} Initiatives}
  \resumeSubHeadingListStart
  \resumeSubItem{CLI tool for React Projects}{Setting up a new front-end project is cumbersome and time consuming. Therefore, as a senior developer and a prospective leader, I found it of utmost importance to create a CLI tool that would generate the boilerplate version of app. With intense brainstorming, extensive research and an explicit review of large scale projects, I and other senior developers were able to decide the structure and base architecture for React projects. Once the architecture was finalized I developed the CLI to create components and base structure dynamically. This reduced the set-up time for new frontend projects drastically from initial 3 hours to only 30 minutes.}
  \resumeSubItem{Training session with Team}{Conducted session on Design-Dev review \& Estimations, Git and Effective Google search}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section {{\faGraduationCap} Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Mumbai}{Mumbai, India}
      {Bachelor of Engineering in Information Technology;  First Class}{2010 -- 2015}
      \resumeItemListStart
      \resumeItem{Courses}
       {Data Structures and Algorithms, Software Engineering, Operating Systems, Databases}
       \resumeItemListEnd
  \resumeSubHeadingListEnd


\end{document}