\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{xcolor}
\definecolor{secondary}{HTML}{0D47A1}
\usepackage[T1]{fontenc}

\usepackage[pdfencoding=auto]{hyperref}

\pdfstringdefDisableCommands{%
  \def\faGraduationCap{\unichar{"F19D}}
  \def\faFlask{\unichar{"F0C3}}
  \def\aiGoogleScholar{\unichar{"E9D4}}
  \def\faPieChart{\unichar{"F200}}
  \def\faGears{\unichar{"F085}}
  %
}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.515in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
% \renewcommand{\section}[2]{\vspace{5pt}
%   \colorbox{secondary}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
% }

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\normalsize{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemNoColon}[2]{
  \item\normalsize{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNoColon}[2]{\resumeItemNoColon{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	 \textbf{{\Large Niraj Rajgor}} &
     \href{mailto:nirajr1992@gmail.com}{\faEnvelope \space nirajr1992@gmail.com}\\
     \faPhone \space +91 8097495277 &
     \href{https://medium.com/@nirajrajgor}{\faMedium \space /@nirajrajgor} \space \href{https://www.linkedin.com/in/nirajrajgor/}{\faLinkedin \space /nirajrajgor}\\
\end{tabular*}

\vspace{8pt} % HACK
%-----------ABOUT-----------------
I have 5+ years of experience in architecting \& developing frontend for medium \& large scale applications in a startup environment. I have shouldered responsibilities for project management, requirement analysis, and have been diligently involved in interviewing and recruiting candidates, training new team members and mentoring interns.

%-----------EXPERIENCE-----------------
\section{{\faPieChart} Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
      {Freelance}{Mumbai, India}
      {Senior Software Engineer}{Jul 2020 -- Current}
      \resumeItemListStart
      \resumeItem{Jewelfleet}
       {Architected \& implemented the server-side rendering in React with Redux for a responsive e-commerce application that improved performance \& SEO. Worked on authentication, device identification, filters \& integrated payment gateway. In the team of 2, assigned tasks, performed code reviews \& implemented POCs.}
      \resumeItemListEnd

      \vspace{2mm}
      \resumeSubheading
      {Kustard Technologies}{Mumbai, India}
      {Senior Software Engineer}{Apr 2018 -- Apr 2020}
      \resumeItemListStart
       \resumeItem{Digital Signage}
       {Developed \& architected Multitenant application for IoT domain. Managed 2 team members, project timeline and attained high performance with code splitting \& lazy loading.}
       \resumeItem{Prodace}
       {Developed SAAS product that provides an online workspace for film productions. Worked on WebSockets, Web Storage API \& custom HOC for conditional rendering of UI. Successfully launched the product before the timeline which helped the client receive early feedback.}
       \resumeItem{Wings \& Wheels}
       {Undertook full ownership to develop the flight booking platform. For flight search results on the client-side, implemented sort \& filter functionality. Accomplished flexibility in design using custom components \& performance gain by minimizing unnecessary renders using PureComponent.}
       \resumeItem{Support-lib}
       {Implemented the In-house utility for handling form inputs that decreased the development time by approx 5\%.}
       \resumeItem{Simba}
       {Developed a dashboard for an order tracking and analytical platform of a top beer brand in India. It was the first React project that helped us in moving forward with SPA for future projects. Achieved performance improvement for rendering large datasets using the “windowing” technique from initial 3k records to 50k records.}
	   \resumeItemListEnd
      \vspace{1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     \textit{\small Software Engineer} & \textit{\small Mar 2017 -- Mar 2018} \\
      \end{tabular*}\vspace{-5pt}
      \resumeItemListStart
        \resumeItem{RWOF(Tata Mumbai Marathon)}
        {Developed a web-based platform to analyse statistical data \& provide personalized insights to 10K+ runners. Implemented the project in a tight deadline of 1 week for a 10-feet display.}
        \resumeItem{Snappbox}
        {Developed customer and admin platforms for pickup \& delivery of logistics. Implemented key features like RTL for Arabic language, partial saving of form data using Web Storage API, \& integrating Geocoding service.}
        % \resumeItem{Kustard Website}
        % {Collaborated with team members and mentored other developers to launch the website within 8 Weeks. Achieved competitive advantage which bolstered the business to attract 20\% new client enquiries.}
        \resumeItem{Exrup}
        {Designed and developed dashboard for a SAAS product of digital business cards. Worked on implementation of responsive business card layout, reCAPTCHA and excel export.}
      \resumeItemListEnd

      \vspace{2mm}
      \resumeSubheading
      {LiveFiesta}{Mumbai, India}
      {Frontend Developer}{July 2016 -- Jan 2017}
      \resumeItemListStart
      \item {Designed and developed web app for event ticketing platform to transition offline ticket booking experience to online. Executed the entire project flow using Angular 2 and Bootstrap.}
      \item {Accomplished a 10\% increase in ticket sales by running ad campaign, improving UI/UX, \& implementing SEO techniques.}
      \resumeItemListEnd

      \vspace{2mm}
      \resumeSubheading
      {TechGenium}{Mumbai, India}
      {Frontend Developer \& Co-Founder}{Jun 2015 -- May 2016}
      \resumeItemListStart
      \item {Developed multiple web-based products addressing specific needs for small and medium scale businesses.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{{\faGears} Technical Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{Languages \& DB}{Proficient in JavaScript, ES6, CSS, \& HTML. Experience with Node, Express, MySQL, PHP.}
 \resumeSubItem{Frameworks}{React, Redux, Redux-Thunk, React-Bootstrap, jQuery, Wordpress, Angular 2, SCSS, Bootstrap, Flask.}
 \resumeSubItem{Build \& Other Tool}{Git, npm, Webpack, Babel, Bash, Adobe XD.}
 \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------------
\section{{\faFlask} Initiatives}
  \resumeSubHeadingListStart
  \resumeSubItem{CLI Generator}{Developed an In-house tool to scaffold new React projects from 2 hours to 30 minutes.}
  \resumeSubItem{Training Session}{Conducted sessions on Design-Dev review \& Estimations, Git workflow \& Effective Google search.}
  \resumeSubItem{Blogs}{Publishing engaging blogs to share pragmatic knowledge \& profitable skills to thousands of developers.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section {{\faGraduationCap} Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KJSCE, University of Mumbai}{Mumbai, India}
      {Bachelor of Engineering in Information Technology}{}
      % \resumeItemListStart
      % \resumeItem{Courses}
      %  {Data Structures and Algorithms, Software Engineering, Operating Systems, Databases}
      %  \resumeItemListEnd
  \resumeSubHeadingListEnd


\end{document}