%-------------------------
% Resume in Latex
% Author : Niraj Rajgor
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{ragged2e}
\usepackage{fontawesome5}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{brown}\titlerule \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\normalsize{
		\textbf{#1}{: #2}
	}\vspace{-2pt}
}

\newcommand{\resumeItemText}[1]{
	\item\normalsize{
		{#1}
	}\vspace{-2pt}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemText}[1]{\resumeItemText{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{http://bit.ly/36dHrz9}{\Large Niraj Rajgor}} & \href{mailto:nirajr1992@gmail.com}{nirajr1992@gmail.com}\\
		\href{https://github.com/nirajrajgor}{\faGithub/nirajrajgor}\quad\href{http://bit.ly/2SEX3b9}{\faLinkedin/narayan-acharya}\quad\href{http://bit.ly/36dHrz9}{\faGlobe/nirajrajgor.com} & +1 (631) 307 6395 \\
	\end{tabular*}
	
	% -----------RECENT PROJECTS-----------------
	% \section{Recent Coursework Highlights}
	% \resumeSubHeadingListStart
	% \resumeSubItem{Natural Language Processing}
	% {Sentiment analysis using DAN \& GRU, Dependency Parsing using Neural Nets, Relationship Extraction using GRU \& CNN, Detecting toxicity in comments using Bi-GRU \& BERT.}
	% \resumeSubItem{Data Science}
	% {Predicting Elo ratings of Chess players (Capstone), Fraud detection in transactions.}
	% \resumeSubItem{Computer Vision}
	% {}
	% \resumeSubHeadingListEnd
	
	%-----------EXPERIENCE-----------------
	\section{\faBriefcase \space Professional Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Kustard Technologies}{Mumbai, India}
	{Senior Software Engineer}{Mar 2017 -- Apr 2020}
	\resumeItemListStart
	\resumeItem{Starzomi}
	{It is a distinct platform which allows users (fans) to avail personalized services from celebrities. I collaborated with a junior developer to rewrite the admin panel in SPA. Worked on Celebrity, Order, Service and Permission modules.}
	{Challenges tackled include form builder, custom HOC, permission tree structure and pagination.}
	\resumeItem{Digital Signage}
	{Developed SASS  project that helps the Organization setup and schedule signage applications from the web. Worked on Dashboard and React app which runs on Raspberry pi. Challenged tackled includes role based auth system, Drag and drop feature and Running multiple media in a loop for specified time. Conducted regular stand-up meetings with the entire team in order to ensure effective communication and timely delivery.}
	\resumeItem{Prodace}
	{Developed a SASS product that provides online workspace for film productions. Challenges tackled include handling file upload with any file type, push notification using websockets, handling of UI based on user permission. I was imparted full responsibility as the sole frontend developer on this project and was also actively involved in the decision making process for project design. The project was successfully completed in a span of just two months.}
	\resumeItem{Hbits}
	{Developed a mobile responsive real estate ownership platform where users can buy a percentage of the commercially listed property.
	After purchase user is provided with a dashboard to track it’s progress and monitor the statistics.
	Worked on the consumer panel along with one other junior developer.
	Challenges tackled include working with scroll position, dynamic property ownership tracker, Customizing the graph as per design and updating graph data on user input.
	Additionally, I  developed an APIs to be consumed by both consumer and admin panels.
	The project was completed in three months and was production ready.}
	\resumeItem{Wings \& Wheels (Travel portal)}
	{Developed flight booking platforms that allows users to check flight fares, flight availability and select a best deal for both domestic and international destinations.
		The project was completed in two and half months even though being the only front end developer working on the project.
		Since we did not use any library, it was quite challenging to write all the functionality from scratch.
		Some of the Challenges tackled include airport search dropdown, Handling one way \& return booking logic, Managing Dynamic details of passengers and ability to Pre select the best flights for round trips.
	}
	\resumeItem{Simba}
	{Developed Order tracking and Analytical platform for a famous beer brand in India. The software provides a digitalized way of managing insightful information regarding daily operations and analyzes historical data.
	I was entrusted with full responsibility as the sole frontend developer on the project as well as managing the project team, resolving problems, communicating between team members to ensure timely delivery in order to meet the project deadline.
	Challenged tackled include customizing mix chart, implementing expanded state of item inside table layout, Global search and role based auth system.
	}
	\resumeItemListEnd

	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small Software Engineer} & \textit{\small July 2015 -- Jan 2018} \\
		 \end{tabular*}\vspace{-5pt}
	\resumeItemListStart
	\resumeItem{Runners wall of fame(Marathon)}
	{Developed login based platform to analyse the statistical data of runners such as category rank, running pace, running speed, prediction time, finishing time over the last 5-10 years to provide personalized insights to the runners. Developed login based stats plarform to allow participants to view their historical marathon data and provided insights through graphs and numbers.
	The timeline of project was very tight around 7-8 days but we managed to complete it within time.
	}
	\resumeItem{Snappbox}
	{Worked on implemeting RTL for Arabic language.}
	\resumeItem{Wazza}
	{}
	\resumeItem{Exrup}
	{It's a SASS product for Digital business card. Developed MVC application and took full responsibility for frontend and design of dashboard. The major module includes Organization signup, employee details, selection and customizing business card and also worked on Landing page. Challenged tackled include responsive business card layout, implementing color picker, implementing ReCaptacha and Excel export of employee data.}
	\vspace{-2mm}
	\resumeSubHeadingListEnd
	
	\resumeSubheading
	{LiveFiesta}{Mumbai, India}
	{Frontend Developer}{July 2016 -- Jan 2017}
	\resumeItemListStart
	\item
	{Designed and developed PWA for Event Ticking platform in Angular 2. This helped in moving Ticket booking experience from offline to online.} % Technical features included payment gateway integration, push notifications, deep linking, Google Analytics.} %Leveraged MVP Architecture pattern along with design principles like dependency injection and others for clean, testable and maintainable code.}
	\item
	{Took full responsibilities of the project and implemented the entire flow. Worked on Social Signup, Login, Search Events, Payment and Analytics modules.} %Another application tracked delivery of physical tickets. It helped delivery crew with logistics through Google Maps integration and business with auditing of physical tickets.}
	%\resumeItem{App Design}
	%\item{Designed initial version of the app using UI/UX principles, iconography, \& typography.}
	\vspace{-2mm}
	\resumeSubHeadingListEnd
	
	%\resumeSubheading
	%{TechGenium}{Mumbai, India}
	%{Software Developer \& Partner}{Jun 2015 -- May 2016}
	%Developed mobile and web-based products addressing specific needs of small and medium scale businesses. % Undertook project management responsibilities that included tasks like requirements analysis, project draft and proposal and tracking project timelines and deadlines. Actively involved in team building, interviewing candidates for design and technology roles and training new hires and mentoring interns. %
	
	\resumeSubHeadingListEnd
	
	%-----------TEACHING EXPERIENCE-----------------
	% \section{Prior Teaching Experience}
	% \resumeSubHeadingListStart
	% \resumeSubheading
	% {Department of Information Technology, KJSCE}{Mumbai, India}
	% {Seminar on 'Introduction to Spring Framework}{Mar 2019}
	% \resumeSubheading
	% {Riidl (Research Innovation Incubation Design Labs)}{Mumbai, India}
	% {Android App Development Course in collaboration with Riidl}{Jul 2015 -- Aug 2015}
	% \resumeSubheading
	% {Department of Information Technology, KJSCE}{Mumbai, India}
	%{Lectures for course 'Open Source Mobile Programming: Android'}{Oct 2014}
	% \resumeSubheading
	% {Computer Society of India, KJSCE}{Mumbai, India}
	% {Technical workshops on Open Source OS (Ubuntu), Android \& Web % Development}{Aug 2013 -- Jun 2014}
	% \resumeSubHeadingListEnd	
	
		%-----------PROJECTS AND ACHIEVEMENTS-----------------
	\section{\faFlask \space Projects \& Awards}
	\resumeSubHeadingListStart
	% \resumeSubItem{Physual (Capstone Project)}
	% {Application generated a 3D scene for visualising Newtonian Mechanics Problems using NLP. Came in 3rd in state level competition Prakalpa 2015 and 2nd in Tatva (2015) for presenting associated research paper.}
	% \resumeSubItemText{Published \textit{Visualization of Mechanics Problems based on Natural Language Processing} in International Journal of Computer Applications (2015).}
	\resumeSubItem{\href{https://apps.apple.com/app/id1229976116}{HoldingWilley \faApple}}{An iOS app for displaying real-time scores, stats \& analysis of cricket matches.}
	% {Developed iOS app for Kustard Technologies Pvt. Ltd. that fetches real time scores for cricket matches around the globe and shows ball by ball updates, full score card and  commentary.}
	%{Developed iOS app for Kustard Technologies Pvt. Ltd. for real time scores of cricket matches. App developed in under 1 month with no prior experience of the iOS framework.}
	\resumeSubItem{\href{https://github.com/narayanacharya6/WaveView}{WaveView \faGithub \space \faAndroid}}{Open-source Android/Java library for rendering and animating sinusoidal waves}
	\resumeSubItem{Video Action Classification}{Compared LSTM v/s SVM for action classification task on the UCF101 data. Used Transfer Learning to compute features for 60000 video frames with limited compute resources.}
	% \resumeSubItemText{Relation Extraction on reduced subset of SemEval-2010 Task 8 dataset using GRU and CNN.}
	%\resumeSubItem{Scene Recognition}{Leveraged Deep Learning coupled with Transfer Learning using CNN-based models for scene recognition with 89\% accuracy.}
	% \resumeSubItem{Sentence Representations}{Understanding sentence representations using Perturbation Analysis on sentiment analysis task with IMDb movie reviews using neural networks DAN and GRU.}
	%\resumeSubItem{Pose Estimation}{Estimated 3D pose co-ordinates of humans by regressing over their known 2D co-ordinates using Neural Networks on the Human36M dataset.}
	% \resumeSubItem{Word Embeddings}{Reported comparisons of word embeddings learnt using Cross Entropy Loss v/s Noise Contrastive Estimation Loss by measuring their performance on the word analogy task.}
	\resumeSubItemText{Ranked among top 1\% in India in Graduate Aptitude Test in Engineering for Computer Science, a national-level exam organized by Indian Institute of Technology \& Indian Institute of Sciences.}% among more than 115,000 students in Computer Science.}
	%\resumeSubItem{Course Projects}
	%{\textit{NLP:} Detecting toxicity in online conversations using Deep Learning, Relationship Extraction, Sentiment Analysis, \textit{Data Science:} Predicting Elo ratings of Chess players using play-by-play moves, \textit{Computer Vision:} Action Recognition using LSTM, Pose Estimation, Scene Recognition.}
	%\resumeSubItem{MOOCs}
	%{Mathematics for Machine Learning, Interactive Programming in Python, Game Dev in C\#.}
	% \resumeSubItem{Academic Excellence} %
	%  {Among top 10 students in department during undergrad and $ subject topper for courses 'Programming for Mobile \& Remote Computers', 'Object Oriented Analysis \& Design' \&  'Simulation \& Modeling'.} %
	% \resumeSubItem{Extra-Curricular Activities}
	% {Served as Joint General Secretary for Computer Society of India, KJSCE (2013-14) and was responsible for organizing and delivering workshops and events for students.}
	\resumeSubHeadingListEnd
	
	%-----------PUBLICATIONS-----------------
	\section{\faGraduationCap \space Publication}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Visualization of Mechanics Problems based on Natural Language Processing}{}
	{International Journal of Computer Applications}{Apr 2015}
	\resumeSubHeadingListEnd
	
	%--------PROGRAMMING SKILLS------------
	\section{\faBolt \space Technical Skills}
	\resumeSubHeadingListStart
	\item{
		\textbf{Languages \& DB}{: Proficient in Python \& Java, experience with Swift, C, C++, SQL, NoSQL, MongoDB}}
	\vspace{-8pt}
	\item{
		\textbf{Frameworks \& Libraries}{: Spring, Android, iOS, Apache Kafka, Elastic, Logstash, Kibana, TensorFlow, Keras, PyTorch, NLTK, spaCy, OpenCV, Pandas, NumPy, scikit-learn, Matplotlib, MapReduce, Spark.}}
	\vspace{-8pt}
	\item{
		\textbf{Build \& Other Tools}{: Git, Gradle, Maven, Jenkins, Bash, Linux.}}
	\resumeSubHeadingListEnd

	%-----------EDUCATION-----------------
	\section{\faUniversity \space Education}
	\resumeSubheading
	{University of Mumbai}{Mumbai, India}
	{Bachelor of Engineering in Information Technology; First Class}{Aug 2010 -- May 2015}
	\resumeSubHeadingListStart
	\item{Data Structures \& Algorithms, Software Engineering, Object Oriented Analysis \& Design}
	\resumeSubHeadingListEnd
	\vspace{-8pt}
	\resumeSubHeadingListEnd
	
	%\begin{center}
	%	\small This resume was updated last on \today. Latest version can be found at \href{http://bit.ly/358iDar}{\textit{bit.ly/358iDar}}
	%\end{center}
	
	
	%-------------------------------------------
\end{document}