\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{xcolor}
\definecolor{secondary}{HTML}{0D47A1}
\usepackage[T1]{fontenc}

\usepackage[pdfencoding=auto]{hyperref}

\pdfstringdefDisableCommands{%
  \def\faGraduationCap{\unichar{"F19D}}
  \def\faFlask{\unichar{"F0C3}}
  \def\aiGoogleScholar{\unichar{"E9D4}}
  \def\faPieChart{\unichar{"F200}}
  \def\faGears{\unichar{"F085}}
  %
}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
% \renewcommand{\section}[2]{\vspace{5pt}
%   \colorbox{secondary}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
% }

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\normalsize{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemNoColon}[2]{
  \item\normalsize{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNoColon}[2]{\resumeItemNoColon{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	 \textbf{{\Large Niraj Rajgor}} &
     \href{mailto:nirajr1992@gmail.com}{\faEnvelope \space nirajr1992@gmail.com}\\
     \faPhone \space +91 8097495277 &
     \href{https://www.linkedin.com/in/amanpreet-singh-k}{\faLinkedin \space /nirajrajgor}\\
\end{tabular*}

\vspace{8pt} % HACK
%-----------ABOUT-----------------
I have a 5 years of experience building software and working with cutting edge technologies like React, Redux, Angular, jQuery, Bootstrap, SCSS, Python, Flask, MySQL.
I have close to 5 years of startup experience, so i know what it means to wear many hats, still ship code in response to user needs and changing market situation and all the while still bootstrapping.
I have works in diffrent domain over the course of my carrier ranging from Logistics, Airline, Media \& Entertainement, Real estate, and Electronic signage.
I have been activelty involved in Hiring, Conducting interviews, Mentoring, Training new joinee and performing Code reviews.


%-----------EXPERIENCE-----------------
\section{{\faPieChart} Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Kustard Technologies}{Mumbai, India}
      {Senior Software Engineer}{Feb 2018 -- Apr 2020}
      \resumeItemListStart
       \resumeItem{Starzomi}
       {It is a distinct platform which allows users (fans) to avail personalized services from celebrities. I collaborated with a junior developer to rewrite the admin panel in SPA. Worked on Celebrity, Order, Service and Permission modules. Challenges tackled include form builder, custom HOC, permission tree structure and pagination.}
       \resumeItem{Digital Signage} 
       {Developed SASS  project that helps the Organization setup and schedule signage applications from the web. Worked on Dashboard and React app which runs on Raspberry pi. Challenged tackled includes role based auth system, Drag and drop feature and Running multiple media in a loop for specified time. Conducted regular stand-up meetings with the entire team in order to ensure effective communication and timely delivery.}
       \resumeItem{Prodace}
       {Developed a SASS product that provides online workspace for film productions. Challenges tackled include handling file upload with any file type, push notification using websockets, handling of UI based on user permission. I was imparted full responsibility as the sole frontend developer on this project and was also actively involved in the decision making process for project design. The project was successfully completed in a span of just two months.}
       \resumeItem{Hbits}
       {Developed a mobile responsive real estate ownership platform where users can buy a percentage of the commercially listed property. After purchase user is provided with a dashboard to track it’s progress and monitor the statistics. Worked on the consumer panel along with one other junior developer. Challenges tackled include working with scroll position, dynamic property ownership tracker, Customizing the graph as per design and updating graph data on user input. Additionally, I  developed an APIs to be consumed by both consumer and admin panels. The project was completed in three months and was production ready.}
       \resumeItem{Wings \& Wheels (Travel portal)}
       {Developed flight booking platforms that allows users to check flight fares, flight availability and select a best deal for both domestic and international destinations. The project was completed in two and half months even though being the only front end developer working on the project. Since we did not use any library, it was quite challenging to write all the functionality from scratch. Some of the Challenges tackled include airport search dropdown, Handling one way \& return booking logic, Managing Dynamic details of passengers and ability to Pre select the best flights for round trips.}
       \resumeItem{Simba}
       {Developed Order tracking and Analytical platform for a famous beer brand in India. The software provides a digitalized way of managing insightful information regarding daily operations and analyzes historical data. I was entrusted with full responsibility as the sole frontend developer on the project as well as managing the project team, resolving problems, communicating between team members to ensure timely delivery in order to meet the project deadline. Challenged tackled include customizing mix chart, implementing expanded state of item inside table layout, Global search and role based auth system.}
	   \resumeItemListEnd
      \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     \textit{\small Software Engineer} & \textit{\small Mar 2017 -- Jan 2018} \\
      \end{tabular*}\vspace{-5pt}
      \resumeItemListStart
        \resumeItem{Runners wall of fame(Marathon)}
        {Developed login based platform to analyse the statistical data of runners such as category rank, running pace, running speed, prediction time, finishing time over the last 5-10 years to provide personalized insights to the runners. Developed login based stats plarform to allow participants to view their historical marathon data and provided insights through graphs and numbers. The timeline of project was very tight around 7-8 days but we managed to complete it within time.}
        \resumeItem{Snappbox}
        {Developed Customer and Admin platform for pickup \& delivery of logistics. Worked on key modules like implemeting RTL for Arabic language, Partial saving of form data at each step, Selecting address location from google maps by searching or moving marker and autofill the form address data based on location selected.}
        \resumeItem{Kustard Website}
        {My primary role was to oversee and mentor other developers working on the project, manage the timeline, perform code review and explain to the junior developer how to write complex codes. Launched the website within 2 months.}
        \resumeItem{Exrup}
        {It's a SASS product for Digital business card. Developed MVC application and took full responsibility for frontend and design of dashboard. The major module includes Organization signup, employee details, selection and customizing business card and also worked on Landing page. Challenged tackled include responsive business card layout, implementing color picker, implementing ReCaptacha and Excel export of employee data.}
      \resumeItemListEnd

      \vspace{2mm}
      \resumeSubheading
      {LiveFiesta}{Mumbai, India}
      {Frontend Developer}{July 2016 -- Jan 2017}
      \resumeItemListStart
      \item {Designed and developed PWA for Event Ticking platform in Angular 2. This helped in moving Ticket booking experience from offline to online.}
      \item {Took full responsibilities of the project and implemented the entire flow. Worked on Social Signup, Login, Search Events, Payment and Analytics modules.}
      \resumeItemListEnd

      \vspace{2mm}
      \resumeSubheading
      {TechGenium}{Mumbai, India}
      {Frontend Developer \& Co-Founder}{Jun 2015 -- May 2016}
      \resumeItemListStart
      \item {Developed web-based products addressing specific needs of small and medium scale businesses.}
      \item {Undertook project management responsibilities that included tasks like requirements analysis, project draft and proposal and tracking project timelines and deadlines.}
      \item {Actively involved in team building, interviewing candidates for technology roles and training new hires and mentoring interns.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{{\faGears} Technical Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{Languages \& DB}{Proficient in Javascript, ES6, CSS, \& HTML, Experience with Python, Node, MySQL, PHP}
 \resumeSubItem{Frameworks}{React, Redux, jQuery, Wordpress, Angular 2, SCSS, Bootstrap, Flask.}
 \resumeSubItem{Build \& Other Tool}{Git, Webpack, Bash, Linux.}
 \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------------
\section{{\faFlask} Initiatives}
  \resumeSubHeadingListStart
  \resumeSubItem{CLI tool for React Projects}{Setting up a new front-end project is cumbersome and time consuming. Therefore, as a senior developer and a prospective leader, I found it of utmost importance to create a CLI tool that would generate the boilerplate version of app. With intense brainstorming, extensive research and an explicit review of large scale projects, I and other senior developers were able to decide the structure and base architecture for React projects. Once the architecture was finalized I developed the CLI to create components and base structure dynamically. This reduced the set-up time for new frontend projects drastically from initial 3 hours to only 30 minutes.}
  \resumeSubItem{Training session with Team}{Conducted session on Design-Dev review \& Estimations, Git and Effective Google search}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section {{\faGraduationCap} Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Mumbai}{Mumbai, India}
      {Bachelor of Engineering in Information Technology;  First Class}{2010 -- 2015}
      \resumeItemListStart
      \resumeItem{Courses}
       {Data Structures and Algorithms, Software Engineering, Operating Systems, Databases}
       \resumeItemListEnd
  \resumeSubHeadingListEnd


\end{document}